Bandit Multiclass Linear Classification: Efficient Algorithms for the Separable Case

### 2019-01-20 ICML-submission/notions-of-linear-separability.tex
Update notions-of-linear-separability.tex
Merged the definition of the weak and the strong separability together

\begin{definition}[Weak linear separability]
\label{definition:weak-linear-separability}
Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
integer, and $\gamma$ be a positive real number. Labeled examples $(x_1, y_1),
(x_2, y_2), \dots, (x_T, y_T) \in V \times \{1,2,\dots,K\}$ are said to be
\emph{weakly linearly separable with a margin $\gamma$} if there exist vectors
$w_1, w_2, \dots, w_K \in V$ such that
\begin{align}
\label{equation:weak-linear-separability-1}
& \sum_{i=1}^K \norm{w_i}^2 \le 1 \; , \\
\label{equation:weak-linear-separability-2}
& \begin{gathered}
\forall t \in \{1,2,\dots,T\} \quad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \\
\ip{x_t}{w_{y_t}} \ge \ip{x_t}{w_i} + \gamma \; .
\end{gathered}
\end{align}
\end{definition}

\begin{definition}[Strong linear separability]
\label{definition:strong-linear-separability}
Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
integer, and $\gamma$ be a positive real number. Labeled examples $(x_1, y_1),
(x_2, y_2), \dots, (x_T, y_T) \in V \times \{1,2,\dots,K\}$ are said to be
\emph{strongly linearly separable with a margin $\gamma$} if there exist vectors
$w_1, w_2, \dots, w_K \in V$ such that
\begin{align}
\label{equation:strong-linear-separability-1}
& \sum_{i=1}^K \norm{w_i}^2 \le 1 \; , \\
\label{equation:strong-linear-separability-2}
& \forall t \in \{1,2,\dots,T\} \qquad \qquad \ip{x_t}{w_{y_t}} \ge \frac \gamma 2 \; , \\
\label{equation:strong-linear-separability-3}
& \begin{gathered}
\forall t \in \{1,2,\dots,T\} \qquad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \\
\ip{x_t}{w_i} \le - \frac \gamma 2 \; .
\end{gathered}
\end{align}
\end{definition}

>>>>

\begin{definition}
[Linear separability]
\label{definition:weak-linear-separability}
Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
integer, and $\gamma$ be a positive real number. 
We say that labeled examples $(x_1, y_1),
(x_2, y_2), \dots, (x_T, y_T) \in V \times \{1,2,\dots,K\}$ are 
%said to be
\begin{enumerate}
\item
\emph{weakly linearly separable with a margin $\gamma$} if there exist vectors
$w_1, w_2, \dots, w_K \in V$ such that
\begin{align}
\label{equation:weak-linear-separability-1}
& \sum_{i=1}^K \norm{w_i}^2 \le 1 \; , \\
\label{equation:weak-linear-separability-2}
& \begin{gathered}
\forall t \in \{1,2,\dots,T\} \quad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \\
\ip{x_t}{w_{y_t}} \ge \ip{x_t}{w_i} + \gamma \; ,
\end{gathered}
\end{align}
\item
\emph{strongly linearly separable with a margin $\gamma$} if there exist vectors
$w_1, w_2, \dots, w_K \in V$ such that
\begin{align}
\label{equation:strong-linear-separability-1}
& \sum_{i=1}^K \norm{w_i}^2 \le 1 \; , \\
\label{equation:strong-linear-separability-2}
& \forall t \in \{1,2,\dots,T\} \qquad \qquad \ip{x_t}{w_{y_t}} \ge \frac \gamma 2 \; , \\
\label{equation:strong-linear-separability-3}
& \begin{gathered}
\forall t \in \{1,2,\dots,T\} \quad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \\
\ip{x_t}{w_i} \le - \frac \gamma 2 \; .
\end{gathered}
\end{align}
\end{enumerate}
\end{definition}
